Insert the article title here

### 2018-08-13 writeup/manuscript.tex
edits in cinema bar!
add mention to mindfullness study

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target category or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed `super-searchers' showed no switch cost.

@@

>>>>

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target category or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed `super-foragers' showed no switch cost. This study has been run on ipad touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)[IN PREP], with super-foragers present in both versions. While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}. The data from this study will be re-analysed below to give us an estimate for the reliability of the mouse-click foraging task used in the present study.

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../Scripts/scratch/cor_comparison.pdf}
\caption{Lots of correlations!}
\label{fig:all_the_cor}
\end{figure*}
